PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-03-03 qfenv_paper/qf_environment.tex
SMF section edits finished and started QF section edits

To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions, as done in \cite{Moustakas:2013aa} and discussed 
in the review \cite{Johnston:2011aa}. 
The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
The equation above is the same as Equation 3. in \cite{Moustakas:2013aa} other than the use of $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, which is used because of edge effect 
considerations along the edges of the survey. 
$w_i$ represnts the statistical weight of each galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the 
stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.

$V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe each galaxy $i$ given the apparent magnitude limits of the survey.
However in Section \ref{sec:edgeeffect} we remove the galaxies that lie on the edge of from the target sample. 
In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$ to a what we will refer to as $V_{\rm{max,avail},i}$.

To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$, and $z$ (not to be confused with the ransack sample in Section \ref{sec:edgeeffect}) 
within the target fields and the redshift limits of the surveys.
We then impose the same edge effect cut-off used on the target galaxy population, described in Section \ref{sec:edgeeffect}, onto this random sample. 
For each redshift bin $j$ out of the $n_{\rm{bin}}$ redshift bins, we compute the fraction of the random points that remain in the bin after the points near the edges are removed: 
$f_{\rm{edge},j}$.
Finally we calculate: $V_{\rm{max,avail},i} = V_{\rm{max},i} \times f_{\rm{edge},j}$. 
The $V_{\rm{max},i}$ values in the equation above are computed following the method described in \cite{Moustakas:2013aa} with the same redshift-dependent $K$-correction 
from observed SED and luminosity evolution model.
For more details on computing $V_{\rm{max}}$ we refer readers to Section 4.2 in \cite{Moustakas:2013aa}.

In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
For the PRIMUS target galaxies, we calculate SMFs after excluding one of the target fields each time.
Note in these SMF calculations, the $1/V_{\rm{max},\rm{avail}}$ is corrected for the fact that excluding a field changes the total area of the survey.
Then using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the mass bin; this value is different for each of the stellar mass bins since not all mass bins have galaxies from all five target fields.
$\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jack knife $\Phi^j$s.

Since the SDSS-{\em GALEX} data are contained in one field, we first divide the field into a $30 \times 20$ rectangular grid and then only keep the sectors with at least $100$ galaxies in them. 
Then we use the same method as above to compute the uncertainties through the jack knife technique. 
The panels in the top two rows of Figure \ref{fig:smf} show the SMFs with uncertainties for all $30$ subsamples using aperture with dimensions $R_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.

%Multiple apertures Additionally, we employ multiple apertures, as listed in Table \ref{tab:aperture}, since we are interested in probing the density environment at various scales. 
%Each aperture size will result in a different environment classification; so, $18$ SMFs are generated separately for every aperture we employ.

%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
%galaxies evolves little for all stellar masses and the SMF of star-forming 
%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.

\subsection{Quiescent Fraction} \label{sec:qf_const}
In the last section, we calculated the SMFs for all subsamples of the target galaxies classified by star-forming/quiescent, environment, and redshift. 
In this section, we use the $\Phi$ calculated for each subsample above to compute their respective $\rm{QF}$s: 
\begin{equation}
\rm{QF} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin $\Delta(\rm{log} \: \mathcal{M})$ (Equation \ref{eq:phi}) for the quiescent and star-forming subsamples, respectively.
A value for the $\rm{QF}$ is not assigned in stellar mass bins where either the star-formation subsample or the quiescent subsample do not have any galaxies. 
The bottom panels of Figure \ref{fig:smf} shows the $\rm{QF}$s for the different redshift bins and environment density classifications.

>>>>

To calculate the SMFs we employ a non-parametric 
$1/{V_{\rm{max}}}$ estimator commonly used for 
galaxy luminosity functions and stellar mass functions
, as done in \cite{Moustakas:2013aa} and discussed 
in the review \cite{Johnston:2011aa}. The differential 
SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
The equation above is same as Equation 3. in 
\cite{Moustakas:2013aa} except for the distinction that 
we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, 
to account for the edge effects of the survey for our
environment measurements. $w_i$ here represents 
the statistical weight of each galaxy $i$ and 
$\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ 
is the number of galaxies ($N$) per unit volume within the 
stellar mass range 
$[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.

$V_{\rm{max},i}$ is the maximum cosmological volume 
where it is possible to observe galaxy $i$ given the apparent 
magnitude limits of the survey. However in Section \ref{sec:edgeeffect} 
we remove the galaxies that lie on the edge from our sample. 
In doing so we reduce the maximum cosmological volume 
where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$.

To calculate $V_{\rm{max,avail},i}$, we generate a sample of 
points with random $RA$, $Dec$ within the window function of 
the target sample and $z$ in the redshift range. This is not to be 
confused with the ransack sample in Section \ref{sec:edgeeffect}. 
We then impose the same edge cuts we applied to the target 
galaxy population. At redshift bins of $\Delta z \sim 0.01$, we 
compute theraction of random points that remain in the bin after 
the edge cuts: $f_{\rm{edge}}$. Afterwards we apply this factor to 
compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. 
The $V_{\rm{max}}$ in the equation above are computed following 
the method described in \cite{Moustakas:2013aa} Section 4.2 with 
the same redshift-dependent $K$-correction from observed SED 
and luminosity evolution model.

In order to calculate the uncertainty of the SMFs from the sample 
variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
For the PRIMUS target galaxies, we calculate SMFs after excluding 
one of the five target fields each time. And for the SDSS target galaxies
we divide the field into a 30 $\times$ 20 rectangular $RA$ and $Dec$ 
grid and calculate the SMFs after excluding part of the field each time. 
Then using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass
bins. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
in each stellar mass bin for all of the jack knife $\Phi^j$s. The SMFs for 
16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
dense/spare environments are presented in Figure \ref{fig:smf}. The 
redshift evolution of the SMFs are indicated by a darker shade for lower
redshifts. The sample variance uncertainties are represented by the 
width of the SMFs. The environment measurements and classifications
for Figure \ref{fig:smf} is done using a cylindrical aperture with dimensions,
$R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.

Examining the SMF evolution over $z \sim 0 - 0.8$, we find that in dense 
environments, the quiescent SMFs increase by a factor of $over9000$ 
for $\mathcal{M}_{*} < 11.0$ while the SMF of the star-forming 
galaxies evolves little for all masses. Meanwhile in low density 
environments from $z=0.8$ to $0.0$, we find that the SMF of 
quiescent galaxies evolves little for all stellar masses and the 
SMF of star-forming galaxies decreases by a factor of $over9000$ 
for $\mathcal{M}_{*} > 10.5$.  
%%% EXPAND ON ANALYSIS OF SMF

\subsection{Quiescent Fraction} \label{sec:qf_const}
Using the SMF number densities ($\Phi$) calculated above, 
in this section, we compute the quiescent fraction, $f_{\rm{Q}}$ 
for dense and sparse environments over the redshift range 
$0.0 - 0.8$.  The quiescent fraction is simply given by the following 
equation: 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies 
per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ 
for the quiescent and star-forming subsamples, respectively 
(Equation \ref{eq:phi}). The bottom panels of Figure \ref{fig:smf} 
shows the evolution of $f_{\rm{Q}}$ for dense (right) and sparse (left)
environments. As before, the darker shades of orange represent 
lower redshift bins.

%%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION
